BarnebyLives: an R package to create herbarium specimen labels and clean spreadsheets

### 2025-07-19 manuscript/BarnebyLives An R package to create and qc herbarium labels.rmd
writing
floating ?function
level

@@

`r long_flag` records were appropriately flagged for issues with auto fill increment of the longitude value, and `r lat_flag` records were also auto-flagged for increases in latitude values.

@@

# ACKNOWLEDGEMENTS 
The Bureau of Land Management is gratefully acknowledged as a provider of funding to R.C.B. for most of his specimen collection activities. 
We thank the two anonymous peer reviewers who have increased the quality of this manuscript.
Several prominent associated collectors of specimens used in this study are thanked: Dani Yashinovitz, Hannah Lovell, Dakota Becerra, Caitlin Miller, Hubert Szczygiel.

@@

# SUPPORTING INFORMATION
Additional supporting information can be found online in the Supporting Information section at the end of this article.

**Appendix S1.** A table of all time trials for each function.

>>>>

# INTRODUCTION

@@

`r long_flag` records were appropriately flagged for issues with auto fill increment of the longitude value, and `r lat_flag` records were also auto-flagged for increases in latitude values. 
All flags were correct, and in several instances more errors were found in the rows following the flagged values.

@@

# ACKNOWLEDGMENTS 
The Bureau of Land Management is gratefully acknowledged as a provider of funding to R.C.B. for most of his specimen collection activities. 
We thank the two anonymous peer reviewers who have increased the quality of this manuscript.
Several prominent associated collectors of specimens used in this study are thanked: Dani Yashinovitz, Hannah Lovell, Dakota Becerra, Caitlin Miller, Hubert Szczygiel.

@@
